\section{Measures and Results}
\label{measures}

% What measures did you apply (brief explanation of how they work)? How do
% they relate to the intent of the study? Why are they relevant? What is the connection among the gathered data, the applied measures,
% and the properties found?\\

For both the Italian and London gangs, we study the same network metrics and compare them. We start by analyzing \textbf{general structural metrics}, which quantify the overall organization and efficiency of the network:

\subsection*{General Structural Metrics}

\begin{itemize}
    \item \textbf{Density ($D$)}: it measures the fraction of all possible edges in the graph that actually exist.
          \begin{equation}
              D = \frac{2m}{n(n-1)}
          \end{equation}
          where $m$ is the number of existing edges and $n$ the number of nodes. In our networks, density reflects how globally interconnected the criminal gang is. High values of density indicate that overall, criminals maintain many direct relationships with other members.

    \item \textbf{Average degree ($\langle k \rangle$)}: the mean number of connections per node.
          \begin{equation}
              \langle k \rangle = \frac{1}{n}\sum_{i=1}^{n} k_i = \frac{2m}{n}
          \end{equation}
          In our networks, it measures the average number of relationships that criminals maintain, capturing their social activity and exposure.

    \item \textbf{Network diameter ($D_{max}$)} and \textbf{average path length ($\ell$)}: respectively, the maximum and the mean of the shortest path distances between all node pairs.
          \begin{equation}
              D_{max} = \max_{i,j} d_{ij}
          \end{equation}
          \begin{equation}
              \ell = \frac{1}{n(n-1)} \sum_{i \neq j} d_{ij}
          \end{equation}
          In our networks, these two measures offer insights into the communication distances between criminals and how efficiently information can propagate through them.

    \item \textbf{Clustering coefficient ($C$)}: expresses the probability that two neighbors of a node are connected, revealing local cohesion or closed ``cells''.
          For node $i$:
          \begin{equation}
              C_i = \frac{2t_i}{k_i(k_i - 1)}
          \end{equation}
          where $t_i$ is the number of triangles passing through $i$. The overall clustering coefficient is the average of $C_i$ across all nodes:
          \begin{equation}
              C = \frac{1}{n} \sum_{i=1}^{n} C_i
          \end{equation}
          In our networks, it measures the cohesivenes of local operational cells formed by interconnected criminals.

    \item \textbf{Modularity ($Q$)}: quantifies the presence of well-defined communities:
          \begin{equation}\label{eq:modularity}
              Q = \frac{1}{2m}\sum_{ij}\left(A_{ij}-\frac{d_j d_i}{2m}\right)\delta(g_i, g_j)
          \end{equation}
          where $m$ is the total number of edges, $A_{ij}$ is the adjacency matrix, $d$ represents node degrees, and $\delta(g_i, g_j)$ is the Kronecker delta (1 if nodes $i$ and $j$ share the same birthplace group, 0 otherwise). In our networks, it captures the extent to which criminals tend to organize themselves into distinct subgroups with limited interaction between them.
\end{itemize}

\subsection*{Centrality Metrics}

We also compute \textbf{centrality metrics}, which identify key actors based on different notions of importance:

\begin{itemize}
    \item \textbf{Degree centrality ($C_D(i)$)}: number of direct ties a node has.
          \begin{equation}
              C_D(i) = k_i
          \end{equation}
          In our networks, it reveals the most active or influential criminals, based on the number of relationships with other members.

    \item \textbf{Betweenness centrality ($C_B(i)$)}: measures how often a node lies on the shortest paths between others.
          \begin{equation}
              C_B(i) = \sum_{s \neq i \neq d} \frac{\sigma_{sd}(i)}{\sigma_{sd}}
          \end{equation}
          where $\sigma_{sd}$ is the number of shortest paths between $s$ and $d$, and $\sigma_{sd}(i)$ those passing through $i$. In our networks, it highlights how much criminals can act as brokers or gatekeepers.

    \item \textbf{Closeness centrality ($C_C(i)$)}: reciprocal of the mean distance from a node to all others.
          \begin{equation}
              C_C(i) = \frac{n-1}{\sum_{j\neq i} d_{ij}}
          \end{equation}
          In our networks, this measure offers insight into how efficiently a criminal can reach, or be reached by, the rest of the gang.

    \item \textbf{Eigenvector centrality ($C_E(i)$)}: assigns importance based on being connected to other important nodes.
          \begin{equation}
              C_E(i) = \frac{1}{\kappa}\sum_{j=1}^{n} A_{ij} C_E(j)
          \end{equation}
          where $\kappa$ is the largest eigenvalue of the adjacency matrix $A$. It identifies leaders recognized by other influential members and, in our networks, it measures how embedded a criminal is within the main core structures of the organization.
\end{itemize}

\subsection*{Roles and Network Hierarchy}

Based on these metrics, we classify network roles as follows:

\begin{itemize}
    \item \textbf{Leaders}: nodes in the top 5\% for both degree and eigenvector centrality, broadly connected and influential.
    \item \textbf{Brokers}: nodes in the top 5\% for betweenness, key intermediaries between subgroups.
    \item \textbf{Peripherals}: nodes in the bottom 5\% for degree, few connections and limited influence.
\end{itemize}

We further analyze the \textbf{\textit{k}-core decomposition} to inspect hierarchical structure and power concentration.
A $k$-core is a maximal subgraph where each node has degree $\geq k$.
The \textit{main core} corresponds to the highest $k$ with non-empty core.

We also assess \textbf{network robustness} by comparing metrics (density, average path length, $k$-core) before and after removing central nodes, in order to study the structural impact of node removal.

\subsection*{Attribute-based Network Analysis}

Finally, to explore how ethnic background shapes internal organization, we perform \textbf{attribute-based network analyses} based on the \textit{Birthplace} attribute.

\begin{itemize}
    \item \textbf{Assortativity (Modularity $Q$) and mixing matrix}: used to quantify the extent of homophily by \textit{Birthplace}. For unordered characteristics, assortativity is measured as the modularity $Q$ [\ref{eq:modularity}] indicating the extent to which similar nodes connect to each other.

    \item \textbf{Centrality by group}: comparing average degree, betweenness, and eigenvector centrality across ethnic categories reveals whether certain groups occupy more central positions.

    \item \textbf{Community composition and diversity}: community detection via modularity maximization; ethnic heterogeneity measured with the \textbf{Shannon Diversity Index}:
          \begin{equation}
              H = - \sum_i p_i \log(p_i)
          \end{equation}
          where $p_i$ is the proportion of members from group $i$ within a community. Higher $H$ values indicate more diverse communities.

    \item \textbf{Inter-group connectivity}: proportion of edges linking individuals of different birthplace categories, indicating cross-ethnic integration.

    \item \textbf{Subgraph analysis by birthplace}: evaluation of intra-group cohesion through internal density and clustering coefficient.
\end{itemize}

\textit{Note:} Since the Italian network is disconnected, metrics such as diameter and average path length are computed on the largest connected component, including cases where central nodes are removed.